Patient-Specific Neural Field Model

### 2010-07-11 ltx/data_paper/DataPaper.tex
added spatial freq figure
added LFP figure and some pre-processing steps

@@

\subsection{Data Collection}
\begin{itemize}
	\item Show medical imaging
	\item Show LFP Data (background, seizure, post-seizure)
	\item Show spectral properties of LFPs
\end{itemize}

@@

\subsection{Pre-processing}

\subsection{Estimation Algorithm}
\begin{itemize}
	\item Model
	\item URTSS
\end{itemize}

>>>>

\usepackage{amsmath,amssymb,amsfonts,epsfig} % Typical maths resource packages

@@

\subsection{Data Collection}
\begin{itemize}
	\item Show medical imaging
	\item Show LFP Data (background, seizure, post-seizure)
	\item Show spectral properties of LFPs
\end{itemize}
\begin{figure}[!ht]
\begin{center}
\includegraphics{./Figures/LFPs.eps}
\end{center}
\caption{{\bf Local Field Potentials}. Data recorded from the first five channels of the array. The red dotted line indicates the seizure onset and the blue dashed line indicates the seizure end.}
\label{fig:SpatialFreqObservation}
\end{figure}

@@

\begin{figure}[!ht]
\begin{center}
\includegraphics{./Figures/SpatialFreq.eps}
\end{center}
\caption{{\bf Spatial frequency analysis of the observed neural field}. A. Pre-seizure observations. B. Seizure observations. C. Post-seizure observations.}
\label{fig:SpatialFreqObservation}
\end{figure}

\subsection{Pre-processing}
\begin{itemize}
	\item Identification and removal of bad channels
	\item Common average reference (CAR) montage 
	\item Low-pass filter data, with cut-off at 100~Hz
	\item Decimate data from 30~kHz to 5~kHz temporal sampling
	\item Spatially interpolate missing data to facilitate spatial frequency analysis
\end{itemize}
\subsection{Estimation Algorithm}
\begin{itemize}
	\item Model
	\item URTSS
\end{itemize}
